\item ./appendix/assets/charts/fitnessLogger.drawio.  
\item ./appendix/assets/charts/fitnessLogger.png.  
\item ./appendix/assets/charts/fitnessLogger.jpg.  
\item ./appendix/assets/img/backendBacklog.jpg.  
\item ./appendix/assets/img/flTemplateTree.png.  
\item ./appendix/assets/img/frontendBacklog.jpg.  
\item ./appendix/assets/img/initialRequirementDocument.jpg.  
\item ./appendix/assets/img/journalEntries/ex1.jpg.  
\item ./appendix/assets/img/journalEntries/ex3.jpg.  
\item ./appendix/assets/img/journalEntries/ex2.jpg.  
\item ./appendix/assets/img/journalEntries/ex4.jpg.  
\item ./appendix/assets/img/flTpTypesTree.png.  
\item ./appendix/assets/img/uiDesigns/excersisePage.jpg.  
\item ./appendix/assets/img/uiDesigns/workoutsPage.jpg.  
\item ./appendix/assets/img/uiScreenShots/trackingPointNewSet.jpg.  
\item ./appendix/assets/img/uiScreenShots/trackingPointNewSingleValue.jpg.  
\item ./appendix/assets/img/uiScreenShots/trackingPointNewTypeList.jpg.  
\item ./appendix/assets/img/uiScreenShots/loginScreen.jpg.  
\item ./appendix/assets/img/uiScreenShots/workoutStopDialogue.jpg.  
\item ./appendix/assets/img/uiScreenShots/workoutEditNotesDialogue.jpg.  
\item ./appendix/assets/img/uiScreenShots/workoutScreen.jpg.  
\item ./appendix/assets/img/uiScreenShots/typeDeletionDialogue.jpg~.  
\item ./appendix/assets/img/uiScreenShots/toBeImplementedToast.jpg.  
\item ./appendix/assets/img/uiScreenShots/toBeImplementedToast.jpg~.  
\item ./appendix/assets/img/uiScreenShots/homeScreen.jpg.  
\item ./appendix/assets/img/uiScreenShots/typeEditScreen.jpg.  
\item ./appendix/assets/img/uiScreenShots/newWorkout.jpg.  
\item ./appendix/assets/img/uiScreenShots/trackingPointNew.jpg.  
\item ./appendix/assets/img/uiScreenShots/typeNewScreen.jpg.  
\item ./appendix/assets/img/uiScreenShots/typesListScreen.jpg.  
\item ./appendix/assets/img/uiScreenShots/typeDeletionDialogue.jpg.  
\item ./appendix/assets/img/uiScreenShots/workoutsListScreen.jpg.  
